---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {linkrot}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

An R package to help detect [linkrot](https://en.wikipedia.org/wiki/Link_rot), which is when links to a web page break because it's been taken down or moved.

Very much a concept for now. Feel free to contribute.

## Install

This package is only available on GitHub. Install from an R session with:

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("matt-dray/linkrot")
```

## Example

Pass a webpage URL to `lr_check()` and get a tibble with each https link on that page and what its [response code](https://developer.mozilla.org/en-US/docs/Web/HTTP/Status) is (ideally we want `200`). 

Here's a check on one of my older blog posts:

```{r}
library(linkrot)
page <-  "https://www.rostrum.blog/2018/04/14/r-trek-exploring-stardates/"
lr_check(page)
```

Uh oh, at least one is broken: it has a `response_code` of `404`.

You could iterate over multiple pages with {purrr}:

```{r}
pages <- c(
  "https://www.rostrum.blog/2018/04/14/r-trek-exploring-stardates/",
  "https://www.rostrum.blog/2018/04/27/two-dogs-in-toilet-elderly-lady-involved/",
  "https://www.rostrum.blog/2018/05/19/pokeballs-in-super-smash-bros/"
)

library(purrr)
set_names(map(pages, lr_check), basename(pages))
```

Uh-oh, more broken links.

## Code of Conduct

Please note that the {linkrot} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
